R Notebook

### 2018-03-30 analysis/final_analysis.Rmd
Preliminary analyses of new data

```{r}
d_raw <- read_tsv('../data/final/experiment2/pilot0/chatMessage/pilot0_messages.csv')

# nonNativeSpeakerIDs <- unique((tangramSubjInfo %>% filter(nativeEnglish != "yes"))$gameid)
incompleteIDs <- unique((d %>% group_by(gameid) %>% 
                           filter(length(unique(trialNum)) != 24))$gameid)

@@

```{r}
d %>%
  filter(hidden == 'no') %>%
  group_by(gameid, context) %>%
  summarize(m = mean(numRawWords)) %>%
  spread(context, m) %>%
  mutate(diff = close - far) %>%
  ggplot(aes(x = far, y = close)) +
    geom_point() +
    theme_bw() +
    geom_abline(intercept = 0, slope = 1) +
    ylim(1,12) +
    xlim(1,12) +
    theme(aspect.ratio = 1)

  summarize(m = mean(numRawWords), se = sd(numRawWords)/sqrt(length(numRawWords))) %>%
    spread(context, numRawWords)

@@

```{r}
d %>%
  group_by(gameid, context, hidden) %>%
  summarize(m = mean(numRawWords)) %>%
  spread(hidden, m) %>%
  mutate(diff = yes - no) %>%
  ggplot(aes(x = no, y = yes)) +
    geom_point() +
    facet_wrap(~ context) +
    theme_bw() +
    geom_abline(intercept = 0, slope = 1) +
    ylim(1,12) +
    ylab('# words (with occlusions)') +
    xlab('# words (without occlusions)') +
    ggtitle('Within-pair comparisons of reference w/ and w/out occlusion') +
    xlim(1,12) +
    theme(aspect.ratio = 1)

@@

```{r}
d %>%
  group_by(gameid, context, hidden) %>%
  summarize(m = mean(numRawWords)) %>%
  spread(hidden, m) %>%
  mutate(diff = yes - no) %>%
  group_by(context) %>%
  summarize(m = mean(diff), se = sd(diff)/sqrt(length(diff))) %>%
  ggplot(aes(x = context, y = m)) +
    geom_bar(stat = 'identity') +
    geom_errorbar(aes(ymin = m - se, ymax = m + se), width = 0) +
    theme_few() +
    ylim(-3, 3) +
    ylab('# words (occlusions - no occlusions)')

@@

# Regression

@@

```{r}
library(ggthemes)
library(lme4)
library(lmerTest)

d.regression <- d %>% 
  unite(condition, context, hidden) %>%
  ungroup() %>%
  mutate(condition = ordered(condition, levels = c('far_no', 'close_no', 'far_yes', 'close_yes')))
contrasts(d.regression$condition) <- contr.helmert(4)
summary(lmer(numRawWords ~ condition + (1 + condition | gameid), data = d.regression))
```

```{r}
summary(lmer(numRawWords ~ context * hidden + (1 + context + hidden | gameid), data = d))
```

>>>>

```{r}
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)

d_raw <- read_tsv('../data/final/experiment2/planned_sample/chatMessage/message.csv') %>%
  filter(iterationName == 'planned_sample') %>%
  filter(role == 'speaker')

# nonNativeSpeakerIDs <- unique((tangramSubjInfo %>% filter(nativeEnglish != "yes"))$gameid)
incompleteIDs <- unique((d_raw %>% group_by(gameid) %>% 
                           filter(length(unique(trialNum)) != 24))$gameid)

@@

```{r}
basic.d <- d %>%
  filter(hidden == 'no') %>%
  group_by(gameid, context) %>%
  summarize(m = mean(numRawWords)) %>%
  spread(context, m) %>%
  mutate(diff = close - far)

ggplot(basic.d, aes(x = far, y = close)) +
    geom_point() +
    theme_bw() +
    geom_abline(intercept = 0, slope = 1) +
    ylim(1,12) +
    xlim(1,12) +
    theme(aspect.ratio = 1)
```

Aggregated to difference scores:

```{r}
ggplot(basic.d, aes(x = diff)) +
    geom_histogram(binwidth = 0.25) +
    theme_bw() +
    geom_vline(xintercept = 0) +
    # ylim(1,12) +
    xlim(-4,4) +
    theme(aspect.ratio = 1)

t.test(basic.d$diff)
```

@@

```{r}
hidden.d <- d %>%
  group_by(gameid, context, hidden) %>%
  summarize(m = mean(numRawWords)) %>%
  spread(hidden, m) %>%
  mutate(diff = yes - no)

ggplot(hidden.d, aes(x = no, y = yes)) +
    geom_point() +
    facet_wrap(~ context) +
    theme_bw() +
    geom_abline(intercept = 0, slope = 1) +
    ylim(1,15) +
    ylab('# words (with occlusions)') +
    xlab('# words (without occlusions)') +
    ggtitle('Within-pair comparisons of reference w/ and w/out occlusion') +
    xlim(1,15) +
    theme(aspect.ratio = 1)

@@

Histogram

```{r}
ggplot(hidden.d %>% group_by(context) %>% mutate(m = mean(diff)), aes(x = diff)) +
    geom_histogram(binwidth = 0.33) +
    theme_bw() +
    geom_vline(xintercept = 0, linetype = 2) +
    geom_vline(aes(xintercept = m), color = 'red') +
    facet_wrap(~ context) +
    # ylim(1,12) +
    xlim(-5,5) +
    theme(aspect.ratio = 1)
```

```{r}
hidden.d %>%
  group_by(context) %>%
  summarize(m = mean(diff), se = sd(diff)/sqrt(length(diff))) %>%
  ggplot(aes(x = context, y = m)) +
    geom_bar(stat = 'identity') +
    geom_errorbar(aes(ymin = m - se, ymax = m + se), width = 0) +
    theme_few() +
    ylim(-3, 3) +
    ylab('# words (occlusions - no occlusions)')

@@

# Stats

Simple effect of hidden-ness in 'far' contexts

```{r}
summary(lmer(numRawWords ~ hidden + (1 + hidden | gameid), 
             data = d %>% 
                filter(context == 'far')))
t.test(numRawWords ~ hidden, data = d %>% filter(context == 'far'), var.equal = FALSE)
```

```{r}
summary(lmer(numRawWords ~ context * hidden + (1 + context * hidden | gameid), data = d))
```

@@

```{r}
d.regression <- d %>% 
  unite(condition, context, hidden) %>%
  ungroup() %>%
  mutate(condition = ordered(condition, levels = c('far_no', 'close_no', 'far_yes', 'close_yes')))
contrasts(d.regression$condition) <- contr.helmert(4)
summary(lmer(numRawWords ~ condition + (1 + condition | gameid), data = d.regression))
```
